Analyzing the impact of social attributes on the success of commit integration

### 2017-02-18 Paper/MSRChallenge2017.tex
rewrote the question subsection

\usepackage{booktabs}
\newcommand{\ra}[1]{\renewcommand{\arraystretch}{#1}}

@@

Previous studies have identified a relationship between technical and social 
factors and pull request acceptance. In the interest of understanding if these 
relationship hold with a different success measure such as commit 
integration success, and in order to establish a baseline to compare to, we have created a dataset with technical attributes to be able to analyze the predictiveness of these attributes and its relationship with commit integration success. This way, we are able to create a model

We are afterwards interested in knowing if adding social attributes to this 
predictability model will increase the probability of the model asserting 
correctly future instances by knowing not only technical data about the commit 
being pushed but also social attributes of the developer pushing the changes. Therefore our main research question is presented as follows:
\newline \newline
\textbf{Are the social attributes gathered 
from the Github profiles of developers who push commits, able to 
increase the predictive power of a model created from technical attributes of the pushed commits?}
\newline \newline
Concerning the results of this research question we can also derive parallel important information. For example, we are also interested in knowing what attributes, either from the technical 
background, the social background, and both combined, are the best proxies for 
knowing what will be the success of the commit integration, helping both developers and integrators to find ways to help them check the success likeliness of a commit based on metadata of the commit.

>>>>

\usepackage{booktabs}
\usepackage{verbatim}
\newcommand{\ra}[1]{\renewcommand{\arraystretch}{#1}}

@@

Previous studies have identified a relationship between technical and social 
factors and pull request acceptance. We are interested in understanding if
social factors, that proxy experience, can be used to predict a
a different success measure: continuous integration success.

Therefore our main research question is presented as follows:
\newline \newline
\textbf{Do social attributes, gathered 
from the Github profiles of developers,
allow for more accurate predictions than only using technical data?}
\newline \newline

Depending on the results of this question, we can further explore which
attributes are most important for predicting build integration success.

\begin{comment}
we have created a dataset with technical attributes to be able to analyze the predictiveness of these attributes and its relationship with commit integration success. This way, we are able to create a model
We are afterwards interested in knowing if adding social attributes to this 
predictability model will increase the probability of the model asserting 
correctly future instances by knowing not only technical data about the commit 
being pushed but also social attributes of the developer pushing the changes.
\end{comment}
